Results

### 2024-10-30 Analysis/04_Summarise_results.Rmd
calculate ses

## Making the fancy tables
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
null_table_2d   <- fancy.table(null_differences_2d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_3d   <- fancy.table(null_differences_3d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_4d   <- fancy.table(null_differences_4d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_5d   <- fancy.table(null_differences_5d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_8d   <- fancy.table(null_differences_8d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), c(4, 6)))
```

```{r, echo = FALSE}
rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_3d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_3d, caption = "Results of the model scaled metric ~ removal level per stressor (3D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_emp) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_emp, caption = "Results of the model scaled metric ~ removal level for the empirical data (3D)", align = "c")
```
```{r, echo = FALSE}
rownames(null_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table_2d) <- gsub(".d_rm", ".rm", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("equalizing", "equa", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("facilitation", "faci", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("filtering", "filt", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("competition", "comp", colnames(null_table_2d))
kable(null_table_2d, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2d)", align = "c")
```

>>>>

## Making the fancy tables
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
null_table_2d   <- fancy.table(null_differences_2d, columns = list(c(1,3), c(1,3)+4, c(1,3)+8, c(1,3)+12))
null_table_3d   <- fancy.table(null_differences_3d, columns = list(c(1,3), c(1,3)+4, c(1,3)+8, c(1,3)+12))
null_table_4d   <- fancy.table(null_differences_4d, columns = list(c(1,3), c(1,3)+4, c(1,3)+8, c(1,3)+12))
null_table_5d   <- fancy.table(null_differences_5d, columns = list(c(1,3), c(1,3)+4, c(1,3)+8, c(1,3)+12))
null_table_8d   <- fancy.table(null_differences_8d, columns = list(c(1,3), c(1,3)+4, c(1,3)+8, c(1,3)+12))
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), c(1,3)+4))
```

```{r, echo = FALSE}
rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_3d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_3d, caption = "Results of the model scaled metric ~ removal level per stressor (3D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_emp) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_emp, caption = "Results of the model scaled metric ~ removal level for the empirical data (5D)", align = "c")
```
```{r, echo = FALSE}
rownames(null_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table_2d) <- gsub(".d_rm", ".rm", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("equalizing", "equa", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("facilitation", "faci", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("filtering", "filt", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("competition", "comp", colnames(null_table_2d))
kable(null_table_2d, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2d)", align = "c")
```
